Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-27 main_new.tex
updates

\runauthor{TO. Fossum et al.}

@@

AUVs operate underwater used to gather spatio-temporal data from a
targeted domain, carrying a scientific payload to survey the water
column or the seafloor. They run at $\sim 1-3$ m/s, can reach depths
from 100--6000m. In water staying capacity depends on survey speed,
payload sensors and mission design. By deploying AUVs one can in
principle fill gaps and augment data obtained from either ocean models,
earth observing satellite data, or fixed-location sensors on buoys due
to their speed and mobility. Traditional operations and surveys with
AUVs are usually limited to planning samples along fixed transects or
survey lines set by human operators, programmed as a sequential plan
consisting of different waypoints and depths. But by using on-board
algorithms to continuously evaluate, update, and refine future sampling
locations, making information gathering adaptive \citep{das11b} is
feasible. For instance, an AUV could reconstruct or modify a survey line
based on what temperatures it is measuring by using embedded methods in
decision-theoretic planning \citep{ryan10}.

@@

Determining paths for mobile robotic sensors in order to maximize the
information gained about an environment is formally known as informative
path planning. This, and related problems such as the orienteering
problem \citep{Golden87}, has been studied in the context of graphs,
where the potential measurement are assigned to nodes on which
evaluation of different routes can be conducted.
%In this context, a fundamental result from \cite{nemhauser1978analysis} proves that a simple greedy algorithm (iteratively selecting the location which most increases the utility) can achieve a near-optimal solution if the problem can be shown to be \emph{submodular}\footnote{an intuitive diminishing returns property, where the informative value of adding sensors decrease with the number of sensors added.}. Building on this result, \cite{chekuri2005recursive} explored this in the setting of a graph using a recursive greedy algorithm, providing near-optimal solutions depending on the planning horizon and graph resolution. 
Adaptive sampling of an evolving frontal feature has been explored in \cite{Zhang2012} and \cite{Pinto2018} using state-based autonomous agents. Both approaches use a reactive-adaptive scheme, meaning that the selection does not use a statistical model of the environment in its strategic sampling effort, but rather adapts based on detection and state switching.
Myopic sampling, i.e. step-wise selection of the path (on the graph) which reduces the information criterion the most, has been used for adaptive surveying \citep{singh2009efficient,Binney2013}. These exploration strategies focus largely on reducing predictive variance or mutual information (entropy). Because the variance and entropy reduction are independent of the actual data realizations under the assumption of GP models, the use of data-driven (adaptive) criteria was introduced to include more targeted sampling of interesting regions (hotspot sampling) by \cite{Low2009} and \cite{fossuminformation}.

>>>>

\runauthor{Fossum et al.}

@@

AUVs operate underwater used to gather spatio-temporal data from a
targeted domain, carrying a scientific payload to survey the water
column or the seafloor. They run at $\sim 1-3$ m/s, can reach depths
from 100--6000m with in-water staying capacity depending on survey
speed, payload sensors and mission design. By deploying AUVs one can in
principle fill gaps and augment data obtained from either ocean models,
earth observing satellite data, or fixed-location sensors on buoys due
to their speed and mobility. Traditional operations and surveys with
AUVs are usually limited to planning samples along fixed transects or
survey lines set by human operators, programmed as a sequential plan
consisting of different waypoints and depths. But by using on-board
algorithms to continuously evaluate, update, and refine future sampling
locations, making information gathering adaptive \citep{das11b} is
feasible. For instance, an AUV could reconstruct or modify a survey line
based on what temperatures it is measuring by using embedded methods in
decision-theoretic planning \citep{Rajan12b}.

@@

% Determining paths for mobile robotic sensors in order to maximize the
% information gained about an environment is formally known as informative
% path planning. This, and related problems such as the orienteering
% problem \citep{Golden87}, has been studied in the context of graphs,
% where the potential measurement are assigned to nodes on which
% evaluation of different routes can be conducted.
%In this context, a fundamental result from \cite{nemhauser1978analysis} proves that a simple greedy algorithm (iteratively selecting the location which most increases the utility) can achieve a near-optimal solution if the problem can be shown to be \emph{submodular}\footnote{an intuitive diminishing returns property, where the informative value of adding sensors decrease with the number of sensors added.}. Building on this result, \cite{chekuri2005recursive} explored this in the setting of a graph using a recursive greedy algorithm, providing near-optimal solutions depending on the planning horizon and graph resolution. 
Adaptive sampling of an evolving frontal feature has been explored in
\cite{fronts11,Zhang2012,Pinto2018,costa19} using state-based autonomous
agents. These approaches typically use a reactive-adaptive scheme,
whereby exploration does not rely on a statistical model of the
environment, but rather adapts based on closing the sensing and
actuation loop. Myopic sampling, i.e. step-wise selection of the path
(on the graph) which reduces the information criterion the most, has
been used for adaptive surveys \citep{singh2009efficient,Binney2013} which
focus largely on reducing predictive variance or mutual information
(entropy). Because the variance and entropy reduction are independent of
the actual data realizations under the assumption of GP models, the use
of data-driven (adaptive) criteria was introduced to include more
targeted sampling of interesting regions (hotspot sampling) by
\cite{Low2009} and \cite{fossuminformation}.
